Bridging Gaps: Investigating COVID-19's Influence on Health Disparities in Connecticut

### 2023-10-30 manuscript/manuscript.tex
add limitations

Figure\ref{fig:Income by town.pdf} shows the distance against the speed from this dataset.
\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{Income by year.pdf}
  \caption{This is my first figure.}\label{fig:cars}
\end{figure}

@@

What are the limitations of this study?

>>>>

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{Income by year.pdf}
  \caption{Median Income by Year.}\label{fig:cars}
\end{figure}

\begin{figure}[tbp]
    \centering
    \includegraphics[width=\textwidth]{Income by town.pdf}
    \caption{Median Income by County.}\label{fig:cars}
  \end{figure}

@@

What are the limitations of this study?
One limitation lies in the availability and quality of data. This dataset does not have any 
data from years after 2020 which may serve to limit potential external validity considerations. 
There may also be variability in data collection methods and discrepancies in reporting standards 
leading to missing or incomplete data over the course of 4 years. Another limitation involves the scope 
of the study, focusing on specific counties in Connecticut may not fully capture nationwide disparities. 
Additionally, the research is limited to the factor parameters selected to investigate which  might not 
encompass all relevant social determinants affecting health outcomes.
